k-Space Domain Parallel Transmit Pulse Design

### 2020-08-17 Manuscript/kPtx_paper.tex
WAG comments

\title{Tailored Spiral In-Out Spectral-Spatial Water Suppression Pulses for 
Magnetic Resonance Spectroscopic Imaging}
\author{Jun Ma$^{1,3}$, Carrie Wismans$^{2}$, Zhipeng Cao$^{1}$, Dennis W.J. Klomp$^{2}$, Jannie P. Wijnen$^{2}$\\ and William A. Grissom$^{*1,3}$}
\maketitle
\begin{flushleft}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Radiology, University Medical Centre Utrecht, Utrecht, the Netherlands \\   
$^3$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\

@@

\par
Acknowledgment: This work was supported by NIH R01 EB016695.

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
something
\\[1em]
{\bf Methods:}
something
\\[1em]
{\bf Results:}
something
\\[1em]
{\bf Conclusion:}
something
\\[1em]
{\bf \noindent Key words:} Spectroscopy; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation; Optimization.

>>>>

\title{k-Space Domain Parallel Transmit Pulse Design}
\author{Jun Ma$^{1,2}$ and William A. Grissom$^{*1,2}$}
\maketitle
\begin{flushleft}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\

@@

\par
Acknowledgment: This work was supported by NIH grants R01 EB016695 and U01 EB 025162.

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
To improve the computational efficiency of parallel transmission pulse design. 
\\[1em]
{\bf Methods:}
something
\\[1em]
{\bf Results:}
something
\\[1em]
{\bf Conclusion:}
something
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.
